---
title: "functions"
author: "Yu"
date: "November 6, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
```


## Do somethinf simple

```{r}
x_vec =  rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec))/sd(x_vec)


```


I want a function to comput z-scores

```{r}
z_scores = function(x){
  
  if(!is.numeric(x)){
    stop("Inout must be numeric")
  }
  
  if(length(x)<3){
    stop("Input must has three more numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  return(z)
  
}

z_scores(x_vec)
   

```

Try my function on some other things, These should give errors

```{r, error= TRUE}
z_scores(3)
z_scores('my name is rita')
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```


##Multiple outputs

```{r}
mean_and_sd = function(x){
  
  if(!is.numeric(x)){
    stop("Inout must be numeric")
  }
  
  if(length(x)<3){
    stop("Input must has three more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}


```


Check thtat the funtion works.

```{r}
x_vec = rnorm(100, mean =3, sd = 4)
mean_and_sd(x_vec)
```


##Multiple inputs

I'd like to do this with a function
```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )
sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )

```


```{r}
sim_mean_sd = function(samp_size, mu, sigma){
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma )
  )
sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
  
}

sim_mean_sd(sample_size = 100, mu = 6, sigma = 3)
```


##Let's review Napoleon Dynamite

```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

napoleon_html = read_html(url)

review_titles = 
  napoleon_html %>% 
  html_nodes(".a-text-bold span") %>% 
  html_text()

review_stars = 
  napoleon_html %>% 
  html_nodes('.review-rating') %>% 
  html_text() %>% 
  str_extract("^\\d") %>% 
  as.numeric()

review_text = 
  napoleon_html %>% 
  html_nodes('.review-text-content span') %>% 
  html_text() %>% 
  str_replace_all('\n', "")


review = 
  tibble(
  titles = review_titles,
  stars = review_stars,
  text = review_text
)
```



What about the next page of reviews
Let's turn that code into a function


```{r, eval = FALSE}

read_page_reviews = function(url){
  

html = read_html(url)

review_titles = 
  html %>% 
  html_nodes(".a-text-bold span") %>% 
  html_text()

review_stars = 
  html %>% 
  html_nodes('.review-rating') %>% 
  html_text() %>% 
  str_extract("^\\d") %>% 
  as.numeric()

review_text = 
  html %>% 
  html_nodes('.review-text-content span') %>% 
  html_text() %>% 
  str_replace_all('\n', "")


reviews = 
  tibble(
   titles = review_titles,
   stars = review_stars,
   text = review_text
)

 reviews
}
```


Let me try my function

```{r}
dynamite_url = 'https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2'

read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews

```{r}
dynamite_url_base = url = 'https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber='

dynamite_urls = str_c(dynamite_url_base, 1:50)

all_review = 
  bind_rows(
  read_page_reviews(dynamite_urls[1]),
  read_page_reviews(dynamite_urls[2]),
  read_page_reviews(dynamite_urls[3]),
  read_page_reviews(dynamite_urls[4]),
  read_page_reviews(dynamite_urls[5])
)

```


## Mean scoping example

```{r}
f = function(x){
 z = x+y
 z
 
}

x =1 
y =2

f(x = y)
```


## Functions as argument

```{r}
my_summary = function(x, summ_func) {
  
  summ_func(x)
}

x_vec= rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, IQR)
```

