---
title: "Untitled"
author: "Yu"
date: "November 9, 2020"
output: github_document
---

```{r}
library(tidyverse)
library(purrr)
library(ggplot2)
library(knitr)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6, 
  out.width = '90%'
)

theme_set(theme_minimal() + theme(legend.position = 'bottom'))  #apply this theme setting everywhere in this document

options(
  ggplot2.continuous.color = 'viridis',
  ggplot2.continuous.fill = 'viridis'
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists

You can put anything in a list

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
```


```{r}
l
l$vec_numeric
l[[1]]
mean(l[["vec_numeric"]])
```


##`for` loop

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = .2),
    d = rnorm(20, mean = -3, sd = 1)
  )
```


```{r}
list_norm[[1]]
list_norm
```


Pause
```{r}
mean_and_sd = function(x){
  
  if(!is.numeric(x)){
    stop("Inout must be numeric")
  }
  
  if(length(x)<3){
    stop("Input must has three more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

I can apply that function to each list element.

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```


Let's use for loop:

```{r}
output=vector('list', length = 4)
 

for(i in 1:4){

output[[i]] = mean_and_sd(list_norm[[i]])
 
}                        
                        
```

##Let's try map!

```{r}
output = map(list_norm, mean_and_sd)
```


what if you want t different funtion..?

```{r}
output = map(list_norm, IQR)
```


```{r}
output = map_dbl(list_norm, median, .id = 'input')


```

```{r}
output = map_df(list_norm, mean_and_sd, .id = 'input')
```


## List columns!
```{r}
listcol_df = 
  tibble(
    name = c('a', 'b', 'c', 'd'),
    samp = list_norm
  )
```

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

list_df %>% 
  filter(name == 'a')
```

Let's try some operations.

```{r}
mean_and_sd(listcol_df$samp[[1]])
mean_and_sd(listcol_df$samp[[2]])
mean_and_sd(listcol_df$samp[[3]])
mean_and_sd(listcol_df$samp[[4]])

```

Can I just ..map?

```{r}
map(listcol_df$samp, mean_and_sd)
```

So ... can I add a list column??

```{r}
listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd),
    median = map_dbl(samp, median)
  )
```


## Weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Get our list columns ..

```{r}
weather_nest = 
  weather_df %>% 
  nest(data = date:tmin)
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)

weather_nest$data[[3]]
```


Suppose i want to regress 'tmax' on 'tmin' for each station.

This works ...
```{r}
lm(tmax ~ tmin, weather_nest$data[[1]])
```


Let's write a function.

```{r}

weather_lm = function(df){ 
  lm(tmax ~ tmin, data = df)
}

output = vector('list', 3)

for(i in 1:3){
  output[[i]] = weather_lm(weather_nest$data[[i]])
}


```


What about a map..!?

```{r}
map(weather_nest$data, weather_lm)
```


What about a map in a list column!!!?

```{r}
weather_nest = 
  weather_nest %>% 
    mutate(models = map(data, weather_lm))

weather_nest$models
```

